Supplementary Material for Food-web complexity alters the fitness landscape of an insect herbivore

### 2018-06-07 supp_mat_complexity_selection.Rmd

```{r FUNCTIONS}
gamm.model <- function(formula, data) {
  gamm4(formula, data, 
        random = ~(1|Genotype/Plant_Position/Gall_Number), 
        family = binomial(link = logit))
}

gam.plot <- function(gam.model, ...) {
  plot(gam.model, seWithMean = T, shift = mean(predict(gam.model)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
}

>>>>

Custom functions to avoid repetitive code
```{r FUNCTIONS}
gamm.model <- function(formula, data) {
  gamm4(formula, data, 
        random = ~(1|Genotype/Plant_Position/Gall_Number), 
        family = binomial(link = logit))
}

gam.plot <- function(gam.model, ...) {
  plot(gam.model, se = TRUE, seWithMean = T, shift = mean(predict(gam.model)), trans = function(x) {exp(x)/(1+exp(x))}, ...)
}
